### 2021-08-29 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.6

\begin{abstract}
Roaming is the capability of a subscriber to have persistence of service in a mobile network managed by a different operator. To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement. Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase. To address the lack of transparency contained in this stage, this paper proposes the use of a Natural Language Processing engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. In addition to the NLP Engine design, the implementation and testing are carried out as part of an experimentation phase to measure the accuracy at which the output file has been populated.
\end{abstract}

\begin{IEEEkeywords}
Natural Language Processing, NLP, Roaming Agreement, Amazon Comprehend, Similarity
\end{IEEEkeywords}

@@

\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA standard templates.

@@

However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e. the MNOs, still use asynchronous flows such as e-mail or even regular mail for the exchange of information. On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs. On the other hand, this process is a waste of time. As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}. It is necessary to provide a transparent digitization system for RA drafting negotiations, allowing only a few days or even hours to be spent. For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine. This NLP engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The NLP engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts. For this purpose, the NLP engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques. The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool. This article includes not only the design phase, but also the implementation and evaluation of the tool.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitalization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.

Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary. Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement. Therefore, we can affirm that our work introduces a topic with a high degree of novelty.

\section{NLP Engine methodology}
Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement. In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template. In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}. In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}. As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial name of a MNO and the start date of the agreement. The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.

@@

The starting point of the methodology is the detection of PDF files. The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers can be detected. The resources to use to detect are font size and font weight. Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed. Once the parsing phase has been completed, on the one hand, \textit{detection} and on the other hand, \textit{comparison} is performed.

The \textit{detection} phase presents a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol packet the API outputs entities, key phrases and sentiment in a JSON format (\cite{AWS2021}), which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'. In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the element stored in the 'Text' field. Once this filtering is done, the processing is carried out based on sorting forms, for which the designed logic is particularized according to the type of varaibles to be detected. For example, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected variables are stored to be used later to determine which ones are part of the variations.

@@

The \textit{comparison} phase implies a complex pre-processing in order to separate by articles and then in sub-articles. Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template. After that, \textit{Jaccard's similarity} associates a score to the sub-article id. A score greater than 0.85 (score $\geq$ 0.85) is considered a standard clause, a value less than 0.15 (score $\leq$ 0.15) is considered a custom text and a value between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85) is considered a variation. At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation}, the \textit{variables} that it contains.

\section{Implemented System}
The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts. First, the input files include the Roaming Agreement text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.

@@

Regarding the input and output files, these are associated to the container through volumes. In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point. Although the NLP Engine constitutes a library, it must in turn integrate other libraries, among which boto3 \cite{boto3}. Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS). The NLP Engine imports the service associated to Amazon Comprehend. Other library imported into NLP Engine library is PyMuPDF (\cite{PyMuPDF}), which is used by the NLP Engine to extract headers and footers from the PDF files. Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports. Regarding the implementation of the \textit{similarity} it should be noted that it has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.

\section{Discussion of Results}
Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison. The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a variation, a standard clause or a customized text with respect to the GSMA standard template. Additionally, the detected variables are analyzed. The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles. Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each sub-article, i.e., variable, variation, standard clause and custom text. The following confusion matrices allow us to analyze the results for each sample roaming agreements. In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable. Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.

@@

The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement. Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.

Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}. Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted is the greater detection capacity of the NLP Engine in one document with respect to another.

@@

@@

The following radar chart allow us to analyze the results for each roaming agreement. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement. The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement. In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.

@@

\section{Conclusions}
The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as standard clauses, variations and customized texts. The test phase allows to evaluate the results obtained from two types of experiments carried out to measure the accuracy. The results show on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the detection of standard clauses, an accuracy of 82.9\% in the detection of variations and an accuracy of 80\% in the detection of personalized texts. These results improve for the second sample roaming agreement with an accuracy of 92.9\% in the detection of standard clauses, an accuracy of 87.5\% in the detection of variations and an accuracy of 91.2\% in the detection of custom texts. On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols. This result also improves for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols. Therefore, the results demonstrate the feasibility of applying the proposed methodology. Although the results demonstrate the feasibility of the designed methodology, as part of a process of continuous improvement within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity.

>>>>

\begin{abstract}
Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator. To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement. Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase, which on the one hand do not ensure transparency and on the other hand constitute a waste of time with duration of up to one month. To address the lack of transparency and reduce wasted time, this paper proposes the use of a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The Natural Language Processing Engine not only is designed but also is implemented and tested. Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
\end{abstract}

\begin{IEEEkeywords}
Natural Language Processing, Telecommunication, Roaming Agreement, Amazon Comprehend, Similarity
\end{IEEEkeywords}

@@

\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.

@@

However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e. the MNOs, still use asynchronous flows such as e-mail or even regular mail for the information exchange. On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs. On the other hand, this process is a waste of time. As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}. Therefore, it is necessary to provide a transparent digitization system for RA drafting negotiations, which guarantees the use of a few days or even hours. For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine. This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The NLP Engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts. For this purpose, the NLP Engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques. The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool. This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.

Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as judiciary. Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement. Therefore, we can affirm that our work introduces a topic with a high degree of novelty.

\section{NLP Engine methodology}
Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the Roaming Agreement. In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template. In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering and information retrieval problems \cite{7429408}. In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}. As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA. The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.

@@

The starting point of the methodology is the detection of PDF files. The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters. For that purpose, the mechanism used is the detection of different font size and weight. Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed. It is now possible to perform both \textit{detection} and \textit{comparison}.

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol packet the API outputs entities, key phrases and sentiment in a JSON format (\cite{AWS2021}), which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'. In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

@@

The \textit{comparison} phase implies to separate by articles and then by sub-articles. Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template and therefore, to establish comparisons at sub-article level. \textit{Jaccard's similarity} associates a score to the sub-article id. Thus, an sub-article is considered a \textit{standard clause} whether the score assigned is greater than 0.85 (score $\geq$ 0.85). In addition, a sub-article is considered a \textit{custom text} whether the score assigned is less than 0.15 (score $\leq$ 0.15). Finally, a sub-article is considered a \textit{variation} whether the score assigned is between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85). At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation} or \textit{customized texts}, the \textit{variables} that it contains.

\section{Implemented System}
The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts. Thus, the input files include the Roaming Agreement text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.

@@

The input and output files are associated to the container through volumes. In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point. Although the NLP Engine constitutes a library, it must in turn integrate other libraries, among which boto3 \cite{boto3}. Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS). The NLP Engine imports the specific service associated to Amazon Comprehend. PyMuPDF (\cite{PyMuPDF}) constitutes other library imported into the NLP Engine to be used into headers and footers detection. Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports. The \textit{similarity} has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.

\section{Discussion of Results}
Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison. The tests are performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} with respect to the GSMA standard template. The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article. Considering that the results obtained from the simple inspection constitute the observations and the values collected from sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample roaming agreements. In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable. Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives. Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement. Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive. Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document with respect to another.

@@

The following radar chart allow us to analyze the results for each roaming agreement. The radar chart contain in the inner radius the Common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement. The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement. In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.

@@

\section{Conclusions}
The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as \textit{standard clauses}, \textit{variations} and \textit{customized texts}. The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and an accuracy of 80\% in the classification of \textit{customized texts}. These results are improved for the second sample roaming agreement with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}. On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols. This result is also improved for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols. Therefore, the results demonstrate the feasibility of applying the proposed methodology. As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity in order to improve the results obtained.
